### 2021-04-09 assertions/doc/thesis-bernhardt/chapters/2-use_case_analysis.tex
Cost analysis

\section{Cost analysis}
In order to be able to evaluate whether distributed assertion checking can indeed lower the cost in comparison to a local verification, the cost of checking a formula on the blockchain needs to be formalized. Since this thesis describes an implementation of the approach on the Tezos blockchain, the following costs refer to that specific gas model, s.t. the results of the cost analyses are comparable. The gas model of Tezos is described briefly in \secref{sec:tezos}. \\
According to the gas model, the total gas consumption of a transaction $T(src,\, dst=C,\, arg, \, ...)$ to an originated contract $C(storage, \, parameter\, type, \, code)$ is calculated by \eqref{eq:gas_transaction}:
\begin{align}\label{eq:gas_transaction}
\begin{split}
GasConsumed_{transaction} = \quad &read(code) \\
+& \, gasRead(storage) \\
+& \, gasDeserialize(storage, \, arg) \\
+& \, gasParseType(parameter \, type, \, storage) \\
+& \, gasParseData(storage, \, arg) \\
+& \, gasParseCode(code) \\
+& \, gasInterpret(code, \, arg, \, storage) \\
+& \, gasUnparse(storage) \\
+& \, gasSerialize(storage) \\
+& \, gasWrite(storage)
\end{split}
\end{align}
Assuming that the storage is never increased, the amount of gas returned by the cost functions independent of the argument, i.e., the parameter value, remain constant for each $T$. The cost functions for the deserialization, parsing and interpretation, however, are functions of $arg$ that grow strictly monotonic with increasing sizes of $arg$. \\
Consider the following simple contract --- it does not do anything useful, but it can be used to approximate the amplification of the cost functions with regard to $arg$. Appendix \ref{apx:cost_analysis_contract} contains the respective Michelson contract. 
\begin{lstlisting}
contract Foo {
	function bar (int a) public {
		for (uint i = 0; i < a; i++) {
			assert(a == a)
		}
		// ...
	}
}
\end{lstlisting}

>>>>

\section{Cost analysis}
In order to be able to evaluate whether distributed assertion checking can indeed lower the cost in comparison to a local verification, the cost of checking a formula on the blockchain needs to be formalized. Since this thesis describes an implementation of the approach on the Tezos blockchain, the following costs refer to that specific gas model, s.t. the results of the cost analyses are comparable. The gas model of Tezos is described briefly in \secref{sec:tezos}. \\
According to the gas model, the total gas consumption of a transaction $T(src,\, dst=C,\, arg, \, ...)$ to an originated contract $C(storage, \, parameter\, type, \, code)$ is calculated by \eqref{eq:gas_transaction}:
\begin{align}\label{eq:gas_transaction}
\begin{split}
GasConsumed_{transaction} = \quad &read(code) \\
+& \, gasRead(storage) \\
+& \, gasDeserialize(storage, \, arg) \\
+& \, gasParseType(parameter \, type, \, storage) \\
+& \, gasParseData(storage, \, arg) \\
+& \, gasParseCode(code) \\
+& \, gasInterpret(code, \, arg, \, storage) \\
+& \, gasUnparse(storage) \\
+& \, gasSerialize(storage) \\
+& \, gasWrite(storage)
\end{split}
\end{align}
Assuming that the storage is never increased, the amount of gas returned by the cost functions independent of the argument, i.e., the parameter value, remain constant for each $T$. The cost functions for the deserialization, parsing and interpretation, however, are functions of $arg$ that grow strictly monotonic with increasing sizes of $arg$. \\
Consider the following simple contract --- it does not do anything useful, but it can be used to approximate the amplification of the cost functions with regard to $arg$. Appendix \ref{apx:cost_analysis_contract} contains the respective Michelson contract. 
\begin{lstlisting}[numbers=none, language=Solidity]
contract Foo {
	function bar (int a) public {
		for (uint i = 0; i < a; i++) {
			assert(a == a)
		}
		// ...
	}
}
\end{lstlisting}

\begin{lstlisting}[numbers=none, language=Solidity]
contract Spam {
	function ham (int [] b) public {
		for (uint i = 0; i < b.length; i++) {
			assert(b[i] < 10)
		}
		// ...
	}
}
\end{lstlisting}

second contract with more increasing deserialization and parsing costs -> list with the same elements * n; comparable operations
both grow linear and the contract with the list way more due to the increasing deserialization and parsing costs
check protocol version of node + which test network
can we do better with distributed assertion checking?

### 2021-04-09 assertions/doc/thesis-bernhardt/chapters/appendix.tex
Cost analysis

\appendix
\chapter{Assertion Grammar in EBNF}\label{apx:grammar}
The following two versions of the grammar implement the prefix and infix notations for the assertion syntax. 
\todo{Rename mutez}

>>>>

\appendix
\chapter{Michelson contracts used for cost analysis}\label{apx:cost_analysis_contract}

\section{Foo}
\lstinputlisting[basicstyle=\linespread{1.0}\fontfamily{lmr}\selectfont\small,
				 backgroundcolor=\color{cverbbg},
				 linewidth=14cm,
				 xleftmargin=0.5cm,
				 frame=lr,
				 framesep=8pt,
				 framerule=0pt,
				 captionpos=b,
				 numbers=none,
				 language=Michelson,
				 caption=Foo.tz]{listings/foobar.tz} \todo{Caption}

\section{Spam}
\lstinputlisting[basicstyle=\linespread{1.0}\fontfamily{lmr}\selectfont\small,
				 backgroundcolor=\color{cverbbg},
				 linewidth=14cm,
				 xleftmargin=0.5cm,
				 frame=lr,
				 framesep=8pt,
				 framerule=0pt,
				 captionpos=b,
				 numbers=none,
				 language=Michelson,
				 caption=Spam.tz]{listings/spamham.tz} \todo{Caption}

\chapter{Assertion Grammar in EBNF}\label{apx:grammar}
The following two versions of the grammar implement the prefix and infix notations for the assertion syntax. 
\todo{Rename mutez}
